---
output: github_document
---

# decryptr

### Description

`decryptr` is an R package to break CAPTCHAs. It is also an extensible tool
built in a way that enables anyone to contribute with their own CAPTCHA-breaking
code.

To install `decryptr`, simply run the code below:

```{r eval=FALSE}
if (!require(devtools)) install.packages("devtools")
devtools::install_github("decryptr/decryptr")
```

It is also recommended to install `decryptrModels` package.

```{r}
devtools::install_github("decryptr/decryptrModels")
```

### Basic usage

`decryptr` has functions for downloading and breaking captchas from multiple
sources, one of which is TJMG (a court in southern Brazil). Here is how one
could break captchas from TJMG:

#### Download and visualise

```{r captcha, warning=FALSE, message=FALSE}
library(decryptr)

# Download captchas
captcha <- download_tjmg(dest = 'img')

# Draw captcha
captcha %>% 
  read_captcha() %>% 
  plot()
```

#### Classify manually 

```{r eval=FALSE}
captcha %>% 
  read_captcha() %>% 
  classify()
# plots the image and opens the console
#> Answer: 
```

#### Load model and predict

```{r}
# Load model (install decryptrModels package first)
keras_tjmg <- decryptrModels::read_model('tjmg')
data('tjmg', package = 'decryptr')
tjmg$model <- keras_tjmg

captcha %>% 
  read_captcha() %>% 
  predict(tjmg, arq = .)
```

### Performance

Once loaded to memory, Keras models are extremely fast. Also, we don't run any pre-processing on the image.

```{r}
break_captcha <- function() {
  captcha %>% 
    read_captcha() %>% 
    predict(tjmg, arq = .)
}

microbenchmark::microbenchmark(break_captcha())
```

### Extensibility

Since `decryptr` is built on top of S3 methods, anyone can extend its functionalities with custom packages. Simply create a `download_<ext>` function, a `read_<ext>` function, and a `predict.<ext>` function and you're good to go.

More information about extensibility can be found on `decryptr`'s documentation.
